%!TEX TS-program = xelatex  
%!TEX encoding = UTF-8 Unicode

\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage[top=0.7in,bottom=1.0in,left=1.3in,right=1.3in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{fontspec}	
\usepackage[english]{babel}

\setromanfont{Georgia}	

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{\textbf{#1}}\\
  	%\lineover
	\end{changemargin}
}

\newcommand{\contact}[3]{
	\begin{changemargin}{-0.5in}{-0.5in}
		{\Large \textbf{#1}}\\ \smallskip
		\lineover
		\begin{flushright}
			\emph{#2}\\ \smallskip
			\emph{#3}\smallskip
		\end{flushright}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.5in}{-0.5in}
  }
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Wenbin Wang}{ecnuwbwang@gmail.com}{(+86)151-2101-7457}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}

	\textbf{East China Normal University} \hfill \emph{2012/09 - 2015/06}\\
	 Master in Computer Application\\

	\smallskip

	\textbf{East China Normal University} \hfill \emph{2008/09 - 2012/06}\\
	Bachelor in Computer Science and Technology\\
\end{body}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\header{Experience}

\begin{body}
	\vspace{14pt}
	\textbf{Minerva Co. Ltd.} \hfill Full-stack Engineer \emph{2019/04 - } \\
	\smallskip
	As a leader of the delivery team and a key developer, I have been involved from scratch in the completion of multiple projects, including intelligent customer service systems and intelligent approval systems, among others. My responsibility includes communicating with the project manager to understand customer requirements, completing system design, and leading the team to carry out system development, deployment, delivery, and ongoing maintenance.\\
	%作为交付团队领导者和主力研发，从零参与完成了多个项目，包括：智能客服系统，智能审批系统等。负责与项目经理沟通客户的需求，完成系统设计，并且带领团队完成系统开发、部署交付以及后期维护。\\
	\vspace{4pt}
	As the primary developer on the product team, I have been involved from scratch in the development of multiple products, including XiaoXing Assistant (\emph{https://xiaoxing.meinenghua.com}) and the XingYuan \emph{AI+RPA} platform (\emph{https://xingyuan.meinenghua.com}), among others. I was responsible for communicating requirements with the product manager, completing system design, customizing product and development plans, and leading team members to collectively accomplish product development and periodic releases.\\
	%作为产品团队主力研发，从零参与多个产品的研发，包括：小星助手（{\fontarial https://xiaoxing.meinenghua.com}），星原{\fontarial AI+RPA}平台（{\fontarial https://xingyuan.meinenghua.com}）等。负责与产品经理沟通需求，完成系统设计，定制产品计划和研发计划，带领团队成员一起完成产品开发和周期性的发布。\\
	\vspace{4pt}
	I was responsible for the deployment and operations of all projects and products within the company. Addressing common private deployment requirements for B2B clients, I developed a deployment tool that only requires customers to provide a server with a Linux operating system. This tool can complete the installation of basic software and the deployment of application services even in a completely offline environment, reducing the deployment barriers.\\
	%负责公司所有项目和产品的部署运维工作。针对B端客户常见的私有化部署需求，开发了一套部署工具，该工具只需要客户提供装有Linux操作系统的服务器，即便在完全断网的情况下，也能完成基础软件的安装和应用服务的部署，降低部署门槛。\\
	\vspace{4pt}
	Technologies involved: \emph{Vue.js}, \emph{Node.js}, \emph{PostgreSQL}, \emph{Docker}, \emph{Kubernetes}, \emph{Nginx}.
	%涉及技术：{\fontarial Vue.js, Node.js, PostgreSQL, Docker, Kubernetes, Nginx}\\

	\medskip

	\textbf{Microsoft} \hfill Software Engineer \emph{2015/07 - 2019/03} \\
	\smallskip
	I work in the \emph{UCM} team in the \emph{Bing Ads} department. \emph{UCM} is a management tool used by the advertising sales team. My primary job responsibilities include:
	%\smallskip
	%\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Front-end feature development, maintenance, and performance optimization.\\
	\end{itemize}
	%\smallskip
	\vspace*{-8pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Front-end unit test framework enhancement.\\
	\end{itemize}
	\vspace*{-8pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Front-end technology updates, integrating existing code with \emph{React}.\\
	\end{itemize}
	Technologies involved: \emph{jQuery.js}, \emph{Bootstrap.js}, \emph{React}.\\

	%\vspace*{-4pt}
	%\textbf{Multi-round Dialog System} \hfill \emph{2018/06 - 2018/09}\\
	%The system is a task-oriented dialog system based on intent recognition and grooving technology. It adopts micro-service architecture and includes 3 parts: dialog task design, dialog template management and dialog logic processing. The system provides a Web UI that allows administrators to customize dialog templates and provides a chat window for users to engage in multiple rounds of dialogue with the robot. I am responsible for developing the Web UI part of the dialog template management, using React.\\
	\medskip
	
	\textbf{Baidu} \hfill Intern \emph{2013/07 - 2013/10}\\ 
	\smallskip
	I was involved in testing for parts of the \emph{Advertising Manager 2.0}, and I used Selenium to develop automated test cases.
	\medskip
	
	\textbf{Google CSR} \hfill Intern \emph{2012/02 - 2012/08}\\ 
	\smallskip
	
	Work as a web development intern in \emph{CSR Team}. Work on \emph{JSP}, \emph{PHP} and \emph{MySQL}.
	%\smallskip
	\vspace*{-4pt}

	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Response for \emph{www.gong1chuang1.com} daily maintenance and feature upgrades.\\
	\end{itemize}
	\vspace*{-8pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Participated in and completed the website migration from \emph{Java Web} to \emph{PHP}.\\
	\end{itemize}

\end{body}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Honor}
\begin{body}
	\vspace{14pt}
	Bronze Medal, ACM International Collegiate Programming Contest Fuzhou Site. \hfill \emph{2011/11}\\
	Bronze Medal, ACM International Collegiate Programming Contest Beijing Site. \hfill \emph{2011/10}\\
	Honorable Mention, Mathematical Contest In Modeling. \hfill \emph{2011/02}\\
\end{body}

\medskip

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\header{Self-Evaluation}

\begin{body}
	\vspace{14pt}
	I have over 8 years of software development experience, with more than 5 years of full-stack development expertise. Additionally, I have over 3 years of team leadership experience and possess a significant background in system design.\\
	I am focused, diligent, enjoy delving deep into things, and believe that technology changes the world.\\
	\textbf{Skills}: \emph{JavaScript} (proficient), \emph{Python} (familiar), \emph{Go} (currently learning). \\
	\textbf{Languages}: Mandarin {(native speaker)}, English {(CET-6)}\\
\end{body}

\medskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{Hobbies}

\begin{body}
	\vspace{14pt}
	Cooking, badminton, and watching movies.\\
\end{body}

\end{document}
